Run aquaculture model for Atlantic salmon

### 2025-07-23 05_formulating_feeds.qmd
Check for full feeds

There is no check or correction here to ensure that ingredient proportions = 1 in the incoming data. This was checked manually prior to import.

@@

feed_inputs <- feed_input_file %>% 
  read_excel(sheet = "testing") %>% 
  pivot_longer(names_to = "feed", values_to = "proportion", cols = !contains(c("ingredient", "category"))) %>% 
  mutate(feed = as.factor(feed),
         ingredient = as.factor(ingredient)) %>% 
  merge(ingreds, by = "ingredient", all = T)

@@

@@

feed_params <- purrr::map(feed_types, function(ft) {
  df <- feed_inputs %>% 
    filter(feed == ft & proportion != 0) 
  list(
    Proteins = df %>% 
      select(ingredient, proportion, contains("protein"), -contains("feed")) %>%
      rename(macro = protein, digest = protein_digestibility),
    Carbohydrates = df %>% 
      select(ingredient, proportion, contains("carb"), -contains("feed")) %>%
      rename(macro = carb, digest = carb_digestibility),
    Lipids = df %>% 
      select(ingredient, proportion, contains("lipid"), -contains("feed")) %>%
      rename(macro = lipid, digest = lipid_digestibility)
  )
}) %>% 
  setNames(feed_types)
```

>>>>

@@

feed_inputs <- feed_input_file %>% 
  read_excel(sheet = "all_feeds") %>% 
  pivot_longer(names_to = "feed", values_to = "proportion", cols = !contains(c("ingredient", "category"))) %>% 
  mutate(feed = as.factor(feed),
         ingredient = as.factor(ingredient)) %>% 
  merge(ingreds, by = "ingredient", all = T)

@@

Check that ingredient proportions sum to 1.

```{r check-proportions}
#| code-summary: Composition proportions

feed_inputs <- feed_inputs %>% 
  filter(!is.na(proportion) & proportion != 0) %>% 
  group_by(feed) %>% 
  mutate(
    sum = sum(proportion),
    proportion = proportion/sum
  ) %>% 
    ungroup()
```

@@

feed_params <- purrr::map(feed_types, function(ft) {
  df <- feed_inputs %>% 
    filter(feed == ft) 
  list(
    Proteins = df %>% 
      select(ingredient, proportion, contains("protein"), -contains("feed")) %>%
      rename(macro = protein, digest = protein_digestibility),
    Carbohydrates = df %>% 
      select(ingredient, proportion, contains("carb"), -contains("feed")) %>%
      rename(macro = carb, digest = carb_digestibility),
    Lipids = df %>% 
      select(ingredient, proportion, contains("lipid"), -contains("feed")) %>%
      rename(macro = lipid, digest = lipid_digestibility)
  )
}) %>% 
  setNames(feed_types)
```

### 2025-07-23 06_run_atlantic_salmon_model.qmd
Check for full feeds

# Check that the feed will actually work
targets::tar_make(test_reference_feed)
targets::tar_load(test_reference_feed)

# Get harvest sizes for all farms
targets::tar_make(harvest_size)
targets::tar_load(harvest_size)

>>>>

# Check that the feed will actually work
targets::tar_make(test_reference_feed)
targets::tar_load(test_reference_feed)
test_reference_feed # should be ~1430 g

# Get harvest sizes for all farms
targets::tar_make(names = c("harvest_size", "feed_params"))
targets::tar_load(harvest_size)
